### 2020-04-09 learning Logic/draft.tex
a

\documentclass{article}
\usepackage{graphicx,xcolor}
\usepackage{algorithmicx,algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amssymb,amsmath}

@@

@@

>>>>

\documentclass{article}
\usepackage{graphicx,xcolor}
\usepackage{algorithmicx,algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amssymb,amsmath}
\usepackage{tikz}
\usetikzlibrary{automata, positioning, arrows}

\tikzset{
	->, % makes the edges directed
	>=stealth', % makes the arrow heads bold
	node distance=3cm, % specifies the minimum distance between two nodes. Change if necessary.
	every state/.style={thick, fill=gray!10}, % sets the properties for each ’state’ node
	initial text=$ $, % sets the text that appears on the start arrow
}

@@

\begin{algorithm}
	\caption{Current Implementation: MAIN}\label{alg:current_main}
	\begin{algorithmic}[1]
		\State build trivial automaton
		\Repeat
		\State $adviceBDD$=\Call{ask}{$fromStates$} \Comment{Set of good transitions}
		\State sample a bit to find a transition in $adviceBDD$ ($p \rightarrow q$)
		\State \Call{learn}{$p,q$}
		\State $fromStates = fromStates\vee q$
		\Until{sampled all the way to satisfaction of the property}
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}
	\caption{Current Implementation: LEARN}\label{alg:current_learn}
	\begin{algorithmic}[1]
		\Procedure{learn}{$s_1,s_2$}
		\If{$\Call{getLevel}{s_1,s_2}$ $!=3$}\Comment{Possible levels: 0,1,2,3}
		\State $\Call{setLevel}{s_1,s_2,3}$
		\State $DOC^c=\{a\in APSystem\mid \neg(s_1(a)\oplus s_2(a))\}$\Comment{Used for $restrict$}
		\State $R=restrict(s_1,DOC^c)$\Comment{states smilar to $s_1$}
		\State $newTransitions=R \wedge \neg R' \bigwedge\limits_{a\in DOC^c} a\leftrightarrow a' \wedge level=2$
		\State $productAutomaton $ $\vee= (newTransitions \wedge propertyBDD)$
		\EndIf
		\State $counter(s_1)++$
		\If {$counter(s_1)>threshold$}
		\For{$s\in S: (s_1,s) \wedge productAutomataBDD = false$}
		\State \Call{addTransition} {$s_1,s,1$}
		\EndFor
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}
	\caption{Current Implementation: ASK}\label{alg:current_ask}
	\begin{algorithmic}[1]
		\Procedure{ask}{$fromStates$}
		\State $finalStates=$\Call{$findFinalStates$}{$productAutomataBDD\wedge fromStates$}
		\State $reachableStates.add(finalStates)$ 
		\State $reachableStates.add(preFinalStates)$\Comment{required for transition acceptance}
		\State $allReachableStates=currentStates[0]$
		\State $i=1$
		\While{$! (\neg allReachableStates \wedge \Call{pre}{allReachableStates}).isZero()$}
			\State $reachableStates.add(\Call{pre}{reachableStates[i]})$
			\State\Comment{add $(i+1)$th element}
			\State $allReachableStates$ $\vee =reachableStates[i+1]$
			\State $i++$

		\EndWhile
		\State $fromStates$ $\wedge=allReachableStates$
		\State$toState=\Call{img}{fromStates}\wedge reachableStates[i]$
		\State \Return{$getTransitions(fromStates, toStates)$}
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\subsection{A sample run of the algorithm}
